---
title: "Data management graded lab"
author: "Lounès AÏT KARROU"
format: html
editor: visual
---

# MY GITHUB REPOSITORY
Click [here](https://github.com/lllounes/science_fiction.git) to have access to my GitHub repository. 
```{r}
#| message: false
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(here)
library(vroom)
library(stringr)
i_am("science_fiction.Rproj")

```

# CREATION OF THE DATA FILE
```{r}
#| message: false
dir.create("DATAS")
```

```{r}
#| message: false
if (length(list.files("DATAS"))==0) {
filesstrings::file.move("~/Desktop/subject-2/Planets.csv","DATAS")
filesstrings::file.move("~/Desktop/subject-2/star_types.csv","DATAS")
filesstrings::file.move("~/Desktop/subject-2/list+stars.csv","DATAS")
filesstrings::file.move("~/Desktop/subject-2/Yerkes_luminosity_classes.csv","DATAS")
}
```

# LOADING THE DATAS

```{r}
Planets<-vroom(here("DATAS","Planets.csv"))
#validity of the loading process
NumberPlanets<-nrow(Planets)
if (NumberPlanets==998) {Answer='valid'} else {Answer=c('not', ' valid')}
```

Le number of planets in our main data is equal to `r NumberPlanets`, so the loading is `r Answer`  

```{r}
#| message: false
Planets$Planet_key<-as.numeric(Planets$Planet_key)
Planets$Mass<-as.numeric(Planets$Mass)
Planets$Star_number<-as.numeric(Planets$Star_number)
Planets$`relative density`<-as.numeric(Planets$`relative density`)
Planets$`Radius (Earth)`<-as.numeric(Planets$`Radius (Earth)`)
```

# DESCRIPTION OF THE DATA SET

```{r}
NumberVariables<-ncol(Planets)
NumberMiss=vector("numeric",NumberVariables)
for (i in 1:NumberVariables){
  NumberMiss[i]=sum(is.na(Planets[,i]))
}
NumberVariableMiss=0
for (i in 1:NumberVariables){
  if (NumberMiss[i]!=0) {
    NumberVariableMiss=NumberVariableMiss+1
  }
}
```

Study  | Number
------------- | -------------
Observation  | `r NumberPlanets`
Variables  | `r NumberVariables`
Variables with at least one missing value  | `r NumberVariableMiss`
Missing values for `Mass`  | `r NumberMiss[4]`
Missing values for `Radius (Earth)`  | `r NumberMiss[6]`
Missing values for `Type of terrain`  | `r NumberMiss[7]`
Missing values for `Panet key`  | `r NumberMiss[1]`
Missing values for `Name`  | `r NumberMiss[2]`
Missing values for `Star Number`  | `r NumberMiss[3]`
Missing values for `Relative density`  | `r NumberMiss[5]`

# GRAPHICAL REPRESENTATION

```{r,warning=FALSE}
ggplot(Planets|>filter(!is.na(Planets$Mass)),aes(x=`relative density`,y=`Mass`))+
  geom_point() +
  labs(title = "Representation of the mass of a planet as a function of its density",
       x="Relative density",
       y="Mass")
```

# MOST EXTREME PLANET


# EXTRACTION

```{r}
Extraction1<-Planets|>
  reframe(terrain=str_split(`type of terrain`,":"),.by=Planet_key)|>
  unnest(terrain)

Extraction2<-Planets|>
  reframe(climat=str_split(`Climate Type`,":"),.by=Planet_key)|>
  unnest(climat)
```




































